---
title: "BMW Sales Analysis 2010-2024"
format: 
  dashboard
fig-width: 10
fig-asp: 0.3
---

```{r environment setup}
#| label: environment setup
#| include: false 

library(tidyverse)
library(ggplot2)
library(readxl)
library(stringdist)
library(stringr)
library(recipes)
library(FactoMineR)
library(factoextra)
library(gridExtra)
library(patchwork)
library(tidytext)
library(readr)
library(janitor)
library(scales)
library(broom)
library(purrr)
library(forcats)
library(ggrepel)
```

```{r}
#| label: load & preview data 
#| include: false 

df <- read.csv("~/Downloads/BMW sales data (2010-2024).csv", sep=",")

# check a little bit of data to get an idea of what I have on hand 
df%>% head()


# make sure there is no data that is repeated 
distinct(df)


# summary of data 
summary(df)

# checking data types
str(df)
# we want the year data to be in date format 
```

```{r}
#| label: data clean and fns 
#| include: false 

df$date <- as.Date(paste0(df$Year,"-01-01"))
df$fuel_efficiency <-as.factor(df$Engine_Size_L)

df%>%
  group_by(Sales_Classification)%>%
  summarise(top_sales = max(Sales_Volume) )

## if you sell more than 7000 units, then that model in that year will be classified as having high sales 
## anything below that is considered as having low sales 


#standardize column names and generate revenue column and transform engine size from numeric to factor for categorical analysis 
df<- df%>%
  clean_names()%>%
  mutate(revenue = sales_volume*price_usd,
         gasoline_consumption= as.factor(engine_size_l))

# Custom function to format numbers
format_number <- function(x) {
  case_when(
    abs(x) >= 1e12 ~ paste0(round(x/1e12,1), "T"),
    abs(x) >= 1e6 ~ paste0(round(x/1e6, 1), "M"),
    abs(x) >= 1e3 ~ paste0(round(x/1e3, 1), "K"),
    TRUE ~ as.character(x)
  )
}

```

```{r}
#| label: Data prep for valueboxes 
#| include: false 

total_vehicles_sold <- df |>
  summarize(total=sum(sales_volume))|>
  mutate(total = format_number(total))

average_price <- df |>
  summarize(ave_vehicle_price =mean(price_usd))|>
  mutate(ave_vehicle_price = format_number(ave_vehicle_price))

total_revenue <- df |>
  summarise(total_rev =sum(revenue))|>
  mutate(total_rev = format_number(total_rev))
```

# Macro Trends

## Macro Information {height="20%"}

::: {.valuebox icon="car-front-fill" color="#00BFFF"}
Vehicles Sold :

`{r} total_vehicles_sold`
:::

::: {.valuebox icon="currency-dollar" color="#17A2B8"}
Average Cost:

`{r} paste0("$", average_price)`
:::

::: {.valuebox icon="cash-stack" color="#00BFFF"}
Total Revenue Earned:

`{r} paste0("$", total_revenue)`
:::

## Row {height="45%"}

### Sales Distribution across Models {.tabset width="40%"}

```{r}
#| label: Overall 
#| title: Price Distribution of BMW Models 
#| fig-subcap: Arranged in ascending order of Median Price 

  # lets try a box plot over the different models 
df %>%
  ggplot(aes(x = reorder(model, price_usd, FUN = median), y = price_usd)) +
  geom_boxplot(fill = "steelblue", outlier.alpha = 0.5) +
  labs(
    title = "",
    x = "Model",
    y = "Price ($)"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    plot.title = element_text(face = "bold", hjust = 0.5)
  ) +
  scale_y_continuous(labels = scales::dollar) # Format y-axis as dollars
## the average 7 series over the years of analysis is the most expensive of the models under analysis 

```

```{r}
#| label: Price trends over our years of interest across regions where BMWs are sold 
#| include: false

# First, let's create a summary data frame
price_summary <- df %>% 
  group_by(date, region) %>%
  summarise(avg_price = median(price_usd), .groups = 'drop')

# Identify which regions to highlight (replace with your desired regions)
highlight_regions <- c("North America", "Europe", "Asia")

# Create a filtered version for labeling (just the latest date for each region)
label_data <- price_summary %>%
  group_by(region) %>%
  filter(date == max(date))

```

```{r}
#| label: Price Changes v2 
#| title: Vehicles in NA become Expensive as Europe gets Cheaper


# Create the plot
ggplot(price_summary, aes(x = date, y = avg_price, group = region)) +
  # Plot all regions in gray first
  geom_line(data = filter(price_summary, !region %in% highlight_regions), 
            color = "gray70", size = 0.8, alpha = 0.7) +
  # Plot highlighted regions with blue colors
  geom_line(data = filter(price_summary, region %in% highlight_regions),
            aes(color = region), size = 1.5) +
  # Add points for highlighted regions
  geom_point(data = filter(price_summary, region %in% highlight_regions),
             aes(color = region), size = 2, alpha = 0.8) +
  # Add labels only at the end of each line
  geom_text_repel(data = label_data, 
                  aes(label = region, color = region),
                  size = 3.5, direction = "y", box.padding = 0.4,
                  hjust = 0, nudge_x = 30, segment.size = 0.2,
                  show.legend = FALSE) +
  # Custom blue color palette for highlighted regions
  scale_color_manual(values = c("North America" = "darkblue", 
                               "Europe" = "lightblue", 
                               "Asia" = "steelblue")) +
  labs(
    title = "Average Price of BMW Models by Region (2010-2024)",
    x = "Year",
    y = "Price (USD)",
    color = "Highlighted Regions"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    plot.title = element_text(face = "bold", hjust = 0.5, size = 16),
    legend.position = "bottom"
  ) +
  scale_y_continuous(labels = scales::dollar)
## North America BMW's faced a huge increase in price after years in which they were the cheapest
## Asia has the highest prices of BMW's since 2017 
## Europe BMW's prices have been facing downward pressure 

```

### Changes in Prices and Volume over Period of Concern {width="60%"}

```{r}
#| label: Volume and Sales 
#| include: false

df_plot<- df%>%
  group_by(date)%>%
  summarise(total_sales= sum(sales_volume),
            total_revenue= sum (revenue),
            avg_price=mean(price_usd),
            .groups = "drop_last")%>%
  arrange(avg_price)%>%
  ungroup()

 
max_sales <- max(df_plot$total_sales, na.rm = TRUE)
max_price <- max(df_plot$avg_price, na.rm = TRUE)
min_price <- min(df_plot$avg_price, na.rm = TRUE)
price_range <- max_price - min_price


# Set your desired zoom level (e.g., show ±10% of the range)
zoom_factor <- 0.15
desired_min <- min_price- (price_range * zoom_factor)
desired_max <- max_price + (price_range * zoom_factor)
scale_factor <-max_sales / (desired_max - desired_min)
```

```{r}
#| label: Volume and Sales grap
#| title: Price vs Volume over 2010-2024


ggplot(df_plot, aes(x=date))+
  geom_col(aes(y=total_sales),fill="skyblue")+
  geom_line(aes(y=(avg_price - desired_min)*scale_factor),color="blue",size=1.2,lineend="round")+
  scale_y_continuous(
    name="Sales",
    limits = c(0, NA),  # keep sales axis starting at 0
    labels = scales::label_number(scale = 1e-6, suffix = "M"),
    sec.axis=sec_axis(~./scale_factor+desired_min, name="Price ",
                        breaks = scales::pretty_breaks(5),
              labels=scales::dollar))+ 
      labs(
    title = "No Concise Relationship Between Price and Volume"
  ) +  
  coord_cartesian(
    ylim = c(5e-6, max(df_plot$total_sales, na.rm = TRUE) * 1.1)
  ) +
  guides(
    fill = guide_legend(override.aes = list(alpha = 1)),  # Solid color swatches
    color = guide_legend(override.aes = list(linetype = 1, shape = 16))  # Lines + points
  ) +
  theme_minimal(base_size = 14) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    plot.title = element_text(face = "bold", hjust = 0.5),
    panel.grid.minor = element_blank(),
    legend.position = "top"
  ) 


```

## Revenue {height ="35%"}

```{r}
#| label: Revenue 
#| title: Since Covid Revenue Has Been Fluctuating A lot More 

df|> 
  group_by(date)|>
  summarise(revenue_by_year=sum(revenue))|>
  ungroup()|>
  ggplot((aes(date,revenue_by_year)))+
   geom_rect(aes(xmin = as.Date("2020-01-01"), 
                xmax = max(date),
                ymin = -Inf, ymax = Inf),
            fill = "lightgray", alpha = 0.2) +
  geom_line(color="lightblue",size =1.5)+
  geom_point(alpha=.8, color="blue")+
  geom_vline(xintercept =as.Date("2020-01-01"), linetype = "dashed", color = "blue", linewidth = 1)+
    scale_y_continuous( labels = label_dollar(scale = 1e-9, suffix = "B"))+
  labs(title="Revenue Trend",
    x="",y="Revenue ")+
  theme_minimal()+
   theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    plot.title = element_text(face = "bold", hjust = 0.5, size = 16),
    legend.position = "bottom"
  ) 
  
```

# Volume Trends

## Statistics {height= "20%"}

```{r}
#| label: Sale Figures 
#| include: false 
df_sales <- df |>
  group_by(date) |>
  summarize (sales_by_year= sum(sales_volume),
             volatility_in_sales = var(sales_volume),
             average_sales_per_year= mean(sales_volume))

df_sales_final <- df_sales|>
  summarize(volatility_in_sales = sqrt(median(volatility_in_sales)),
            average_sales_per_year= median(sales_by_year))|>
  mutate (average_sales_per_year= format_number(average_sales_per_year))

df_sales_v2 <- df |>
  group_by(date) |>
  summarize (sales_by_year= sum(sales_volume)) |>
  mutate(average_sales_per_year =mean(sales_by_year),
         volume_diff = sales_by_year - average_sales_per_year,
         volume_diff= volume_diff,
         date=  as.factor(lubridate::year(date)),
         volume_diff_Squared = volume_diff*volume_diff)

volatility_in_sales<-format_number(sqrt(sum(df_sales_v2$volume_diff_Squared)/14))

```

::: {.valuebox icon="car-front-fill" color="#00BFFF"}
Vehicles Sold Annually:

`{r} df_sales_final$average_sales_per_year`
:::

::: {.valuebox icon="arrow-down-up" color="#17A2B8"}
Volume Volatility on Annual Basis:

`{r} volatility_in_sales`
:::

## Difference in Sales from Average per year {height="40%"}

### Sales Changes {width ="35 %"}

```{r}
#| label: graph to analyse change of sales from average 
#| title: Extreme Swings in Sales since Covid except 2021 
#| fig-subcap: Annual Sales in year X - Average Annual Sales   

ggplot(df_sales_v2, aes(x=date, fill = volume_diff>0))+
  geom_col(aes(y=volume_diff))+
  geom_hline(yintercept = 0, linetype = "solid", color = "black", size = 0.5)+
  geom_hline(yintercept = 435e3, linetype = "dashed", color = "salmon", size = 0.5)+
   geom_hline(yintercept = -435e3, linetype = "dashed", color = "salmon", size = 0.5)+
   scale_fill_manual(values=c("TRUE"="lightblue", "FALSE" ="navyblue"))+
  scale_y_continuous(labels = format_number)+
  labs(subtitle = "Difference in Sales from Average Sales Per Year",
       x="",
       y="Sales Difference")+
  theme_minimal()+
      theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    plot.subtitle = element_text( hjust = 0.5, size = 16),
    legend.position = "none")
```

```{r}
#|label: data prep for Sales on Fuel Type
#|include: false 

base_year <- as.Date("2010-01-01") 
df_growth <- df %>%
  group_by(fuel_type, date) %>%
  summarise(
    annual_sales = sum(sales_volume, na.rm = TRUE),
    annual_revenue = sum(revenue, na.rm = TRUE),
    avg_annual_price=mean(price_usd,na.rm=T),
    .groups = "drop"
  )%>%
  group_by(fuel_type) %>%
  arrange(fuel_type,date) %>%
  mutate(
    base_price =avg_annual_price[date==base_year],
    price_index = round((avg_annual_price-base_price)/base_price*100,3),
    sales_yoy_growth = round((annual_sales - lag(annual_sales)) / lag(annual_sales),3),
    revenue_yoy_growth = round((annual_revenue - lag(annual_revenue)) / lag(annual_revenue),3),
    sales_yoy_pct = sales_yoy_growth * 100,
    revenue_yoy_pct = revenue_yoy_growth * 100,
    sales_absolute_growth = annual_sales - lag(annual_sales),
    revenue_absolute_growth = annual_revenue - lag(annual_revenue)
  ) %>%
  ungroup()


volatility_df <- df_growth %>%
  group_by(fuel_type) %>%
  summarise(
    volatility = sd(sales_yoy_pct, na.rm = TRUE),
    avg_growth = mean(sales_yoy_pct, na.rm = TRUE)
  ) %>%
  arrange(desc(volatility))


```

### Difference in Sales based on Fuel Type per year {.tabset width="65%"}

```{r}
#| label: Sales based on Fuel Type v1 
#| title: Volatility indicates sensitivity to market conditionsYoY Sales Changes based on Fuel 2010-2024 

  
df_growth %>%
  filter(date >= "2016-01-01") %>%
  ggplot(aes(x = date, y = sales_yoy_pct, color = fuel_type, group = fuel_type)) +
  geom_line(size = 1.2, alpha = 0.8) +
  geom_point(size = 1) +
  scale_color_manual(values = c(
    "Electric" = "navy",
    "Hybrid"  = "blue",
    "Diesel"  = "steelblue",
    "Petrol"  = "turquoise"
  )) +
  labs(
    title = "Year-on-Year Sales Growth by Fuel Type",
    subtitle = "YoY Sales Changes based on Fuel 2010-2024",
    x = "Year", y = "Sales Growth YoY(%)",
    color = "Fuel Type"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    plot.title = element_text(face = "bold", hjust = 0.5),
    legend.position = "top"
  ) +
  geom_hline(yintercept = 0, color = "black", linetype = "solid")+
  geom_hline(yintercept = 5, color = "salmon", linetype = "dashed")+
  geom_hline(yintercept = -5, color = "salmon", linetype = "dashed")


```

```{r}
#| label: Sales based on Fuel Type v2 
#| title: Petrol and Electric Vehicles are More Consistent in Sales 


ggplot(volatility_df, aes(x = volatility, y = avg_growth, label = fuel_type,
                          color = fuel_type)) +
  geom_point(size = 4) +
  geom_text(vjust = -1) +
  scale_color_manual(values = c(
    "Electric" = "navy", "Hybrid" = "blue",
    "Diesel" = "steelblue", "Petrol" = "turquoise"
  )) +
  coord_cartesian(ylim=c(0,.8))+
  labs(
    title = "Growth vs Volatility by Fuel Type",
    subtitle = "High volatility = greater sensitivity; lower = more stable performance",
    x = "Volatility (SD of YoY Growth %)",
    y = "Average Sales Annual Growth (%)"
  ) +
  theme_minimal(base_size = 12) +
  theme(legend.position = "none")


```

## Difference in Sales based on Region Type per year {height="40%"}

### Sales per Region comparing Developed and Developing market {width ="30%"}

```{r}
#| label: Sales per Region prep
#| include: false




df_growth_region <- df %>%
  group_by(region, date) %>%
  summarise(
    annual_sales = sum(sales_volume, na.rm = TRUE),
    annual_revenue = sum(revenue, na.rm = TRUE),
    avg_annual_price=mean(price_usd,na.rm=T),
    .groups = "drop"
  )%>%
    mutate(
    region_group = ifelse(region %in% c("Europe", "North America"), 
                          "High Income Regions", 
                          "Rest of World")
  )%>%
  group_by(region_group, date) %>%
  summarise(annual_sales = sum(annual_sales, na.rm = TRUE), 
            annual_revenue = sum(annual_revenue, na.rm = TRUE),
    avg_annual_price=median(avg_annual_price,na.rm=T),.groups = "drop") %>%
  arrange(date) %>%
  group_by(region_group) %>%
  mutate(sales_yoy_growth = (annual_sales - lag(annual_sales)) / lag(annual_sales) * 100,
    base_price = avg_annual_price[date==base_year],
    price_index = round((avg_annual_price-base_price)/base_price*100,3),
    revenue_yoy_growth = round((annual_revenue - lag(annual_revenue)) / lag(annual_revenue),3),
    sales_yoy_pct = sales_yoy_growth * 100,
    revenue_yoy_pct = revenue_yoy_growth * 100,
    sales_absolute_growth = annual_sales - lag(annual_sales),
    revenue_absolute_growth = annual_revenue - lag(annual_revenue)
  ) %>%
  ungroup()



```

```{r}
#| label: Year-on-Year Sales Growth based on Income Region
#| title: Where is our Market Growing ( Developed vs Developing Market )
#| fig-subcap: Developed Regions  (Europe and North America)


df_growth_region %>%
  filter(date!="2010-01-01")|>
  ungroup()|>
  ggplot(aes(x = date, y = sales_yoy_growth, color = region_group)) +
  geom_line(size = 1.3) +
  geom_point(size = 1.2) +
  scale_color_manual(values = c("High Income Regions" = "steelblue", "Rest of World" = "gray70")) +
  geom_vline(xintercept = as.Date("2020-01-01"), linetype = "dashed",
  color = "salmon") +
  labs(
    title = "Year-on-Year Sales Growth",
    subtitle = "High Income Regions vs. Rest of World",
    y = "YoY Growth (%)",
    x = "Year",
    color = "Region Group"
  ) +
  theme_minimal(base_size = 12)

```

### Changes in Developed and Developing Markets {width ="40%"}


```{r}
#| label: Testing for Correlation period 
#| include: false 
library(zoo)

df_wide <- df_growth_region %>%
  select(date, region_group, sales_yoy_growth) %>%
  pivot_wider(names_from = region_group, values_from = sales_yoy_growth)


# Test multiple windows side-by-side
df_test <- df_wide %>%
  mutate(
    corr_2y = rollapplyr(
      data.frame(`High Income Regions`, `Rest of World`),
      width = 2,
      FUN = function(x) cor(x[,1], x[,2], use = "pairwise.complete.obs"),
      by.column = FALSE,
      fill = NA
    ),
    corr_3y = rollapplyr(
      data.frame(`High Income Regions`, `Rest of World`),
      width = 3,
      FUN = function(x) cor(x[,1], x[,2], use = "pairwise.complete.obs"),
      by.column = FALSE,
      fill = NA
    ),
    corr_5y = rollapplyr(
      data.frame(`High Income Regions`, `Rest of World`),
      width = 5,
      FUN = function(x) cor(x[,1], x[,2], use = "pairwise.complete.obs"),
      by.column = FALSE,
      fill = NA
    )
  )

# Plot all three to compare
ggplot(df_test, aes(x = date)) +
  geom_line(aes(y = corr_2y, color = "2-year"), size = 1) +
  geom_line(aes(y = corr_3y, color = "3-year"), size = 1) +
  geom_line(aes(y = corr_5y, color = "5-year"), size = 1) +
  scale_color_manual(values = c("2-year" = "red", "3-year" = "blue", "5-year" = "green")) +
  labs(title = "Rolling Correlation with Different Windows",
       y = "Correlation",
       color = "Window Size") +
  theme_minimal()

df_wide <- df_wide %>%
  mutate(
    rolling_cor = rollapplyr(
      data.frame(`High Income Regions`, `Rest of World`),
      width = 3,
      FUN = function(x) cor(x[,1], x[,2], use = "pairwise.complete.obs"),
      by.column = FALSE,
      fill = NA
    ))


df_wide |> 
  filter (date >= as.Date("2012-01-01"))|>
  ggplot( aes(x = date, y = rolling_cor)) +
  geom_line(color = "steelblue", size = 1.3) +
  geom_point()+
  geom_vline(xintercept = as.Date("2020-01-01"), linetype = "dashed", color = "red") +
  labs(
    title = "Rolling Correlation: Developed vs Developing Regions",
    subtitle = "Shift from negative to positive correlation post-COVID",
    x = "Year", y = "Correlation"
  ) +
  theme_minimal(base_size = 12)


df_wide <- df_wide %>%
  mutate(
    post_covid = ifelse(date >= as.Date("2020-01-01"), 1, 0),
    time = row_number()
  )

lm_its <- lm(rolling_cor ~ time + post_covid + I(time*post_covid), data = df_wide)
summary(lm_its)


# Plot rolling correlation with fitted ITS trend lines
df_wide <- df_wide %>%
  filter(date>= as.Date("2012-01-01"))|>
  mutate(fitted = predict(lm_its))
```

```{r}
#| label: Correlation Changes  
#| title: How Covid Affects Market Synchronization
#| fig-subcap: How are market moving in relation to each other  

ggplot(df_wide, aes(x = date, y = rolling_cor)) +
  geom_line(color = "steelblue", size = 1.2) +
  geom_line(aes(y = fitted), color = "darkred", linetype = "dashed", size = 1) +
  geom_vline(xintercept = as.Date("2020-01-01"), linetype = "dotted", color = "red") +
  labs(
    title = "Developed vs. Developing Region Synchronization",
    subtitle = "Rolling 5-year correlation in annual sales growth (2010–2025)",
    x = "Year", y = "Rolling Correlation"
  ) +
  theme_minimal(base_size = 12) +
  theme(legend.position = "none")

```
### Models Performance Before, During and After Covid {width ="30%"}

```{r}
#| label: prep data for models 
#| include: false
 
pre_period <- 2015:2019
covid_period <- 2020:2021
post_period <- 2022:2024

df_yoy <- df %>%
  mutate(year = lubridate::year(date)) %>%
  group_by(model, year) %>%
  summarise(annual_sales = sum(sales_volume, na.rm = TRUE), .groups = "drop_last") %>%
  arrange(model, year) %>%
  mutate(yoy_growth = (annual_sales - lag(annual_sales)) / lag(annual_sales) * 100) %>%
  ungroup()


df_volatility_periods <- df_yoy %>%
  group_by(model) %>%
  summarise(
    vol_pre  = sd(yoy_growth[year %in% pre_period], na.rm = TRUE),
    vol_covid = sd(yoy_growth[year %in% covid_period], na.rm = TRUE),
    vol_post = sd(yoy_growth[year %in% post_period], na.rm = TRUE),
    avg_price = mean(df$price_usd[df$model == first(model)], na.rm = TRUE),
    fuel_type = first(df$fuel_type[df$model == first(model)]),
    region = first(df$region[df$model == first(model)]),
    .groups = "drop"
  )

df_volatility_periods <- df_volatility_periods %>%
  mutate(
    covid_vol_ratio = vol_covid / vol_pre,
    post_vol_ratio = vol_post / vol_pre,
    volatility_change = vol_post - vol_pre
  )

df_volatility_periods <- df_volatility_periods %>%
  mutate(
    volatility_pattern = case_when(
      covid_vol_ratio > 1.45 & post_vol_ratio > 1.1 ~ "Persistent Volatility",
      covid_vol_ratio > 1.45 & post_vol_ratio <= 1.1 ~ "Temporary Shock",
      covid_vol_ratio <1 & post_vol_ratio >1.45 ~"Lagged Shock",
      TRUE ~ "Stable"
    )
  )

df_model_perf <- df %>%
  mutate(year = lubridate::year(date)) %>%
  group_by(model) %>%
  summarise(
    avg_sales = mean(sales_volume, na.rm = TRUE),
    total_sales = sum(sales_volume, na.rm = TRUE),
    sales_volatility = sd(sales_volume, na.rm = TRUE),
    cv_sales = sales_volatility / avg_sales,  # coefficient of variation
    fuel_type = first(fuel_type),
    region = first(region),
    .groups = "drop"
  ) %>%
  mutate(
    performance_score = scale(avg_sales) - scale(cv_sales)  # high sales, low volatility
  ) %>%
  arrange(desc(performance_score))


```


```{r}
#| label: Model's performance 
#| title: Performance and Resiliency of Models 
#| fig-subcap: Resiliency = covid volatility/pre-covid volatility 

df_model_perf %>%
  left_join(df_volatility_periods, by = "model")%>%
  select(model,region.x, fuel_type.x, performance_score,vol_pre,vol_covid,
         vol_post,covid_vol_ratio:volatility_pattern)|>
  ggplot(aes(x=performance_score,y=covid_vol_ratio, color=volatility_pattern))+
  geom_hline(yintercept = 1.1, linetype = "dashed") +
  geom_vline(xintercept = 0, linetype = "dashed") +
  geom_point(size = 3, alpha = 0.8) +
  geom_text_repel(aes(label = model), 
                  size = 3, 
                  max.overlaps = 10, 
                  box.padding = 0.35, 
                  segment.color = "grey70") +
  scale_color_manual(values=c(    "Persistent Volatility" = "red",
    "Temporary Shock" = "lightblue",
    "Lagged Shock"="salmon",
    "Stabilized" = "lightblue",
    "Stable" = "deepskyblue"))+
  labs(
    title = "",
    subtitle = "Cross-classifying model performance with pandemic impact",
    x = "Performance Score (Sales Strength + Consistency)",
    y = "COVID Impact on Sales (%)",
    color = "Resilience Category"
  ) +
  theme_minimal()

```

